The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
fix italics

For instance, social scale is major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
Furthermore, it is a common trope that individuals must be associating to
interact, and many studies therefore assume that proximity is proxy for
interacting (Farine, 2015). For instance, baboons need to be in proximity in
order to groom each other. However, animals have certain interactions that do
not require proximity such as long-distance vocalization and olfactory signals
(Carter et al., 2015). With the advancement of biologging technology, we have
the ability to record social interactions that do not require proximity,
particularly long-distance communication networks with devices like microphone
arrays (Snijders & Naguib, 2017). These varying social scales can have different
fitness repercussions for individuals. Rhesus macaques (Macaca mulatta) had
higher survivorship when they had fewer but stronger, more stable social
associates and grooming partners rather than simply more associates (Ellis,
Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights
that different qualities of social scales have lasting consequences.

>>>>

For instance, social scale is major consideration for social network analysis,
especially in the context of different types of relationships, such as grooming
and association, that are typically examined separately while answering a single
question (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015).
Furthermore, it is a common trope that individuals must be associating to
interact, and many studies therefore assume that proximity is proxy for
interacting (Farine, 2015). For instance, baboons need to be in proximity in
order to groom each other. However, animals have certain interactions that do
not require proximity such as long-distance vocalization and olfactory signals
(Carter et al., 2015). With the advancement of biologging technology, we have
the ability to record social interactions that do not require proximity,
particularly long-distance communication networks with devices like microphone
arrays (Snijders & Naguib, 2017). These varying social scales can have different
fitness repercussions for individuals. Rhesus macaques (*Macaca mulatta*) had
higher survivorship when they had fewer but stronger, more stable social
associates and grooming partners rather than simply more associates (Ellis,
Snyder-Mackler, Ruiz-Lambides, Platt, & Brent, 2019). This finding highlights
that different qualities of social scales have lasting consequences.
